Comparative effectiveness of BNT162b2 versus Moderna booster doses in England: protocol

### 2022-05-17 protocol/protocol.Rmd
update protocol / report

  * Lower Layer Super Output Area (LSOA)
  * Middle Layer Super Output Area (MSOA)
  * NHS Strategic Health Partnership (STP)
  * NHS region (East of England, Midlands, London, North East and Yorkshire, North West, South East, South West)

@@

We estimated Kaplan-Meier (KM) cumulative incidence curves separately by vaccine brand, and compared brands using the 10-week risk differences and risk ratios.

Confidence limits for the KM estimate will be derived from complimentary log-log transformation.
Confidence limits for the risk difference will be derived from the square root of the sum of squares the treatment-specific KM standard errors. The KM standard errors will use Greenwood's formula.
Confidence limits for the survival ratio are straight-forward, and can be based on the standard error of the cumulative hazard. But confidence limits for the risk ratio (or relative risk) are more complicated. TBD.

Alternatively, we could bootstrap.

>>>>

  * Lower Layer Super Output Area (LSOA)
  * Middle Layer Super Output Area (MSOA)
  * NHS Sustainability and Transformation Partnership (STP)
  * NHS region (East of England, Midlands, London, North East and Yorkshire, North West, South East, South West)

@@

We estimated Kaplan-Meier (KM) cumulative incidence curves separately by vaccine brand, and compared brands using the 10-week risk differences and risk ratios. The incidence rate ratio (events per person-time-at-risk) in time-period specific intervals will also be reported. This is equivalent to a period-specific hazard ratio if a constant hazard within each time period is assumed.

95% confidence limits for the KM estimates, risk differences, risk ratios, and incidence rate ratios are derived by bootstrapping the matched pairs. 500 bootstrap replicates will be used.

<!-- Alternatively, analytic confidence limits can be derived as follows: Confidence limits for the KM estimate can be derived from complementary log-log transformation. Confidence limits for the risk difference can be derived from the square root of the sum of squares the treatment-specific KM standard errors. The KM standard errors can use Greenwood’s formula. Confidence limits for the survival ratio are straight-forward, and can be based on the standard error of the cumulative hazard. Confidence limits for the risk ratio (or relative risk) are TBD. -->
